### 2016-10-26 paper/intro.tex
minor changes

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that failure-revealing tests
will be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to obtain soundness,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} runs a change-impact
test analysis based on file dependencies computed and maintained at
low cost.

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.  We
assume that the alternative of renting server farms (or even building
one) to mitigate the problem is economically tempting for large IT
organizations but not so for open-source projects and projects of
smaller organizations with lower budgets for building a testing
infrastructure.  As such, this paper studies (1) how relevant the
problem of long-running test suites in open-source software really is,
(2) what are the causes of high execution costs (\eg{}, IO or CPU),
and (3) what is the impact of existing open-source sound approaches to
reducing cost.

>>>>

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that fault-revealing tests will
be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} analyzes which files
that a given test depends on have been impacted by changes. File
dependencies are computed and maintained at low cost.

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.  We
understand that the alternative of renting server farms (or even
building one) to mitigate the regression testing problem is a
potential escape for large IT organizations but not as attractive for
open-source projects and projects from smaller organizations with
lower budgets for building testing infrastructures.  This paper
studies (1) how relevant the problem of long-running test suites in
open-source software is, (2) what are the causes of high execution
cost (CPU vs. IO), and (3) what is the impact of existing open-source
sound approaches to reducing cost.
